%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Event Simulation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Geant3, recombination, drift velocity}

We use GEANT3 for simulating energy deposition of beam particles and
their daughters. Readout pitch is 1 cm, 

we set the maximum step of Geant to 0.5 mm
which is enough smaller than the readout pitch of 1 cm.

It means charge deposition in one strip is typically 
simulated with 20 GEANT steps.

We set energy cut-off for soft electron/photon emission to
10 keV which is minimum possible energy can be set in GEANT3.
This cut-off is very important for  ionization electron recombination.

Recombination of electron and Argon ion depends on
the electric field and $dE/dx$. We use a measurement in Ref.\cite{658352}.
\begin{equation}
Q = A \frac{Q_0}{1 + k dE/dx}, A = 0.800, k = 0.486
\end{equation}

Velocity of the drift electron depends on the liquid Argon temperature
and the electric field. We use a measurement in Ref \cite{649233}.


\begin{verbatim}
 *     Special TPAR for TMED   3   Liquid_argon                                                    *
 *  CUTGAM= 10.00 keV  CUTELE= 10.00 keV  CUTNEU= 10.00 MeV  CUTHAD= 10.00 MeV  CUTMUO= 10.00 MeV  *
 *  BCUTE = 10.00 keV  BCUTM = 10.00 keV  DCUTE = 10.00 keV  DCUTM = 10.00 keV  PPCUTM= 10.00 MeV  *
 *  IPAIR=  1.  ICOMP=  1.  IPHOT=  1.  IPFIS=  0.  IDRAY=  1.  IANNI=  1.  IBREM=  1.  IHADR=  4. *
 *  IMUNU=  1.  IDCAY=  1.  ILOSS=  1.  IMULS=  1.  IRAYL=  0.  ILABS=  0.  ISYNC=  0.  ISTRA=  0. *
\end{verbatim}



\begin{itemize}
\item Plot: Geant Geometry, typical track (Tanaka)
\item Plot: recombination factor, drift velocity  (Tanaka)
\end{itemize}

\subsection{Electric Field}

Electric field of the TPC field cage
We have calculated the electric field using a 2D FEM (Finite Element Method) package \cite{Ref:FEMTET}.

This field map is used for simulating electron drift.


\begin{itemize}
\item Plot: 2D field map  (Tanaka)
\end{itemize}

\subsection{Drift Electron Diffusion}
\begin{itemize}
\item Plot: drift simulation  (Tanaka)
\end{itemize}

\subsection{Preamp Gain Calibration}
\begin{itemize}
\item Preamp gain vs channel number  (Naito)
\end{itemize}

%\subsection{FFT Noise}
\input{./tex/NoiseSim}
\begin{itemize}
\item Plot: simulated event  (Nagasaka)
\end{itemize}

\subsection{Cross Talk}
\begin{itemize}
\item Plot: signal waveform (proton stopped point + 1)  (A. Okamoto)
\item Plot: simulated event with and without cross talk (A. Okamoto)
\end{itemize}

\subsection{Signal and Noise Scale Tuning}
\begin{itemize}
\item Plot: Landau distribution after the tuning  (Tanaka)
\end{itemize}

